Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-29 paper.tex
up

\documentclass{IEEEtran}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}

\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

@@

\textbf{Semantic web Service link}. In Fig. \ref{semanticLink}, $S_{1}$ and $S_{2}$ are linked to together if exists any parameter matchmaking between  Output of $S_1$ and Input of $S_2$.  Therefore, measuring semantic matchmaking quality ($SM$) is to measure the quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$). This semantic web service link is adopt from \cite{lecue2009optimizing}.

>>>>

\documentclass{IEEEtran}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
\usepackage[justification=centering]{caption}
\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

@@

\textbf{Semantic web Service link}. In Fig. \ref{semanticLink}, $S_{1}$ and $S_{2}$ are linked to together if exists any parameter matchmaking between  Output of $S_1$ and Input of $S_2$.  Therefore, measuring semantic matchmaking quality ($SM$) is to measure the overall quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$). This semantic web service link is adopt from \cite{lecue2009optimizing}.
